Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex
Address comments in the evaluation

\noindent\textbf{Setup: }
We assume no prior knowledge on the optimal batch size, learning rate, $\lambda$
or weight decay ($\lambda_2$). Instead, we trained a number of models, randomly
and independently selecting the values of these parameters from a range of
reasonable values (\gl{should we make them explicit ?} \srm{yes}).  
%We trained
%using our modified \texttt{PyTorch} \cite{paszke2017automatic} library that
%supports dynamically resized layers (our code is available at \srm{add
%anonymized link}). 
Training is done using gradient descent and the \textit{Adam}
optimizer \cite{DBLP:journals/corr/KingmaB14}. Specifically, we start with the
learning rate sampled randomly; for every $5$ epochs of non-improvement in
validation accuracy we divide the learning rate by $10$. We stop training after
$400$ epochs or when the learning rate is under $10^{-7}$, whichever comes
first.  \gl{Should I also give the details about the removal strategy we used
and the $\gamma$ and threshold I used ? because this is clearly getting boring}
\srm{probably not necessary} For each of the models we trained, we pick the
epoch with the best validation accuracy and report the corresponding testing
accuracy. Because of the nature of our method, it can happen that for networks
that are aggressively compressed, the best validation accuracy is obtained early
in  training, before the size has converged. To be sure that accuracy measured
corresponds to the final shape and not the starting shape, we only consider the
second half of the training when picking the best epoch. For each model, we also
measure the total size, in terms of number of floating point parameters,
excluding the \textit{Switch Layers} because as described in
\cref{neuron_killing}, these are eliminated after training.

@@

We applied ShrinkNets to the VGG16 network by adding \textit{Switch Layers}
after each \textit{BatchNorm} layer and each fully connected layer (except the
last).  Recall that ShrinkNets assume that the starting size of the network is
an upper bound on the optimal size. For this reason, we simply started with a
network with double the recommended size for each layer as an upper bound (this
is larger than what ImageNet, for example uses). Thus, for the classification
layers we use $5000$ neurons as a starting limit (ImageNet uses $4096$ \gl{This
is on the top of my head, need to be double checked}).

We compare against classical (\textit{Static}) networks. In such networks, the
number of parameters that control the size is large: 13 parameters for the
convolutional layers and $2$ for the fully connected layers. ShrinkNets
effectively fuse all these parameters in a single $\lambda$, but in conventional
architectures where all of these parameters are free, it is infeasible to obtain
a reasonable sample of a search space of this size. For this reason, we rely on
the conventional heuristic that the original VGG architecture (and many CNNs)
\gl{try to find the paper that introduces this heuristic} use, where
\srm{describe what the heuristic is -- doubling of neurons up to apoint?} For
\textit{Static Networks} we sample the size between $0.1$ and $2$ times the size
\srm{size of what?} optimized for ImageNet. \srm{Why are we using ImageNet and
not CIFAR10 as the comparison point?} We report the same numbers as we did for
\textit{ShrinkNets} and we compare the two distributions. \srm{I worry that
this method of selecting network sizes for Static will of course constrain it to
larger sizes and worse performance. What if we just randomly sample networks?
Would it look terrible?}

@@

A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time. \srm{Can we cite something showing that local sparsity does not improve performance even w/ small nets?}, at least for larger batches when hardware can be fully utilized.

@@

\ra{the following is interesting, but how is it related to the above?}
ShrinkNets effectively explores the frontier of model size and accuracy. For a
given target accuracy, the size needed is significantly smaller than when we use the
\srm{name it} heuristic commonly used to size convolutional neural networks.
This suggests that this conventional heuristic may not in fact be optimal,
especially when looking for smaller models.  Empirically we observed this to
often be the case.  For example, during our experimentations on the
\texttt{MNIST} \cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017}
datasets (not reported here due to space constraints), we observed that even
though these datasets have the same number of classes, input features, and
output distributions, for a fixed $\lambda$ \textit{ShrinkNets} converged to
considerably bigger networks in the case of \texttt{FashionMNIST}. This evidence
shows that optimal architecture not only depends on the output distribution or
shape of the data but actually reflects the dataset.  This makes sense, as
\texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.

>>>>

\noindent\textbf{Setup: }
We assume no prior knowledge on the optimal batch size, learning rate, $\lambda$
or weight decay ($\lambda_2$). Instead, we trained a number of models, randomly
and independently selecting the values of these parameters from a range of
reasonable values (\gl{should we make them explicit ?} \srm{yes}).  
%We trained
%using our modified \texttt{PyTorch} \cite{paszke2017automatic} library that
%supports dynamically resized layers (our code is available at \srm{add
%anonymized link}). 
Training is done using gradient descent and the \textit{Adam}
optimizer \cite{DBLP:journals/corr/KingmaB14}. Specifically, we start with the
learning rate sampled randomly; for every $5$ epochs of non-improvement in
validation accuracy we divide the learning rate by $10$. We stop training after
$400$ epochs or when the learning rate is under $10^{-7}$, whichever comes
first. For each of the models we trained, we pick the
epoch with the best validation accuracy and report the corresponding testing
accuracy. Because of the nature of our method, it can happen that for networks
that are aggressively compressed, the best validation accuracy is obtained early
in  training, before the size has converged. To be sure that accuracy measured
corresponds to the final shape and not the starting shape, we only consider the
second half of the training when picking the best epoch. For each model, we also
measure the total size, in terms of number of floating point parameters,
excluding the \textit{Switch Layers} because as described in
\cref{neuron_killing}, these are eliminated after training.

@@

We applied ShrinkNets to the VGG16 network by adding \textit{Switch Layers}
after each \textit{BatchNorm} layer and each fully connected layer (except the
last).  Recall that ShrinkNets assume that the starting size of the network is
an upper bound on the optimal size. For this reason, we simply started with a
network with double the recommended size for each layer as an upper bound (this
is larger than what ImageNet, for example uses). Thus, for the classification
layers we use $5000$ neurons as a starting limit.

We compare against classical (\textit{Static}) networks. In such networks, the
number of parameters that control the size is large: 13 parameters for the
convolutional layers and $2$ for the fully connected layers. ShrinkNets
effectively fuse all these parameters in a single $\lambda$, but in conventional
architectures where all of these parameters are free, it is infeasible to obtain
a reasonable sample of a search space of this size. For this reason, we rely on
the conventional heuristic that the original VGG architecture (and many CNNs)
use, where the number of channels is doubled every after \textit{MaxPool} laxer.
For \textit{Static Networks} we sample the size between $0.1$ and $2$ times the size
original one, optimized for ImageNet. We report the same numbers as we did for
\textit{ShrinkNets} and we compare the two distributions. \srm{I worry that
this method of selecting network sizes for Static will of course constrain it to
larger sizes and worse performance. What if we just randomly sample networks?
Would it look terrible?} \gl {I don't see any pricatical way of sampling
reasonable a 13 dimension space if a single point take 1h to be evaluated}

@@

A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time. \srm{Can we cite something showing that local sparsity does not improve performance even w/ small nets?} \gl{The deep compression in table III shows it very well}, at least for larger batches when hardware can be fully utilized.

@@

\ra{the following is interesting, but how is it related to the above?}
ShrinkNets effectively explores the frontier of model size and accuracy. For a
given target accuracy, the size needed is significantly smaller than when we use the
"channel doubling" heuristic commonly used to size convolutional neural networks.
This suggests that this conventional heuristic may not in fact be optimal,
especially when looking for smaller models.  Empirically we observed this to
often be the case.  For example, during our experimentations on the
\texttt{MNIST} \cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017}
datasets (not reported here due to space constraints), we observed that even
though these datasets have the same number of classes, input features, and
output distributions, for a fixed $\lambda$ \textit{ShrinkNets} converged to
considerably bigger networks in the case of \texttt{FashionMNIST}. This evidence
shows that optimal architecture not only depends on the output distribution or
shape of the data but actually reflects the dataset.  This makes sense, as
\texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.
